---
title: "EpiJSON_Vignette"
author: "Team Hackout2: Thomas Finnae; Andy South; Ellie Sherrard-Smith; Ana Bento"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

This is a demonstration of the package EpiJSON and how you can use the functions provided to change the format of data for use in different analyses.

# Validation

Demonstating how we can go from a JSON character string or object to data frame to an obkData object

Load the required packages as necessary
```{r}

library(devtools)
library(OutbreakTools)
library(sp)
library(HistData)
library(EpiJSON)
```


These are example data in data.frame format

#Example: data frame 1
```{r}
data(Snow.deaths)
```
Adding some dates, pumps, some genders 
```{r}
simulated <- Snow.deaths
simulated$gender <- c("male","female")[(runif(nrow(simulated))>0.5) +1]
simulated$date <- as.POSIXct("1854-04-05") + rnorm(nrow(simulated), 10) * 86400
simulated$pump <- ceiling(runif(nrow(simulated)) * 5)

exampledata1<-head(simulated)
exampledata1
```

#Example: data.frame 2
```{r}
exampledata2<- data.frame(id=c("A","B","3D","4d"),
                 name=c("tom","andy","ellie","Ana"),
                 dob=c("1984-03-14","1985-11-13","1987-06-16","1987-06-16"),
                 gender=c("male","male","female","female"),
                 rec1contact=c(2,1,5,1),
                 rec1dateStart=c("2014-12-28","2014-12-29","2015-01-03","2015-01-08"),
                 rec1dateEnd=c("2014-12-30","2015-01-04","2015-01-07","2015-01-14"),
                 rec1risk=c("high","high","low","high"),  
                 rec1temp=c(39,41,41,39),
                 rec2contact=c(4,1,1,1),
                 rec2dateStart=c("2015-01-02","2015-01-12","2015-01-09","2015-01-09"),
                 rec2risk=c("high","low","high","low"),stringsAsFactors=FALSE)
exampledata2
```

################################################
## Transition 1: data.frame to EpiJSON format ##
################################################

Use the EpiJSON package to convert a data.frame object into a EpiJSON object within R:

```{r}
eg1 <- as.ejObject(exampledata1, recordAttributes = c("gender"), eventDefinitions = list(defineEjEvent(dateStart="date", dateEnd="date", name=NA, location=list(x="x", y="y", proj4string=""), attributes="pump")),
 		metadata=list())
eg1
```

Convert this into a JSON character string
using: eg1a<-r2epiJSON(eg1)


Convert this to a EpiJSON object in R
using: epiJSON2r(eg1a)


```{r}
eg2 <- as.ejObject(exampledata2, recordAttributes = c("name","dob","gender"),
     eventDefinitions = list(defineEjEvent(name="rec1contact",dateStart="rec1dateStart", dateEnd="rec1dateEnd", attributes=list("rec1risk","rec1temp")),
                             defineEjEvent(name="rec2contact",dateStart="rec2dateStart", dateEnd="rec2dateStart", attributes="rec2risk")),
 		metadata=list())
eg2
```

Convert this into a JSON character string
using: eg2a<-r2epiJSON(eg2)


Convert this to a EpiJSON object in R
using: epiJSON2r(eg2a)

#######################################################
## Transition 2: EpiJSON object to data.frame format ##
#######################################################

Use the EpiJSON package to convert a JSON object into a data.frame object:
```{r}
as.data.frame(eg1)
```

#######################################################
## Transition 3: From obkData to an EpiJSON object   ##
#######################################################

These are example data in obkData format
```{r}
data(ToyOutbreak) 
```

Use the EpiJSON package to convert an obkData object to JSON object into :
```{r}
eg3 <- as.ejObject.obkData(ToyOutbreak)
```

#######################################################
## Transition 4: From an EpiJSON object to obkData   ##
#######################################################

*Next function to produce*


#######################################################
## Transition 5: From an EpiJSON object to spatial   ##
#######################################################

Use the EpiJSON package to convert from an EpiJSON object to spatial (sp)
```{r}
example1 <- as.ejObject(simulated, recordAttributes = c("gender"),
     eventDefinitions = list(defineEjEvent(dateStart="date", dateEnd="date", name=NA, location=list(x="x", y="y", proj4string=""), attributes="pump")),
 		metadata=list())

sp_eg1 <- as.SpatialPointsDataFrame.ejObject(example1)

plot(sp_eg1,pch=20,col="green")
text(10,17,"Example from Snow Deaths data")

```

*The story continues...!!!*